### 2023-06-22 manuscript.tex
don't bundle s11's CSS as it refers to fonts [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/e60f158440d0393345a67a362a123fa00df7f8e1.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/e60f158440d0393345a67a362a123fa00df7f8e1/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5340376993

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/6d9233550171f4d9f517b3a485faa60d68c64d34/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/6d9233550171f4d9f517b3a485faa60d68c64d34}{stain/2022-fdo-paper@6d92335}
on June 22, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/e60f158440d0393345a67a362a123fa00df7f8e1/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/e60f158440d0393345a67a362a123fa00df7f8e1}{stain/2022-fdo-paper@e60f158}
on June 22, 2023.
